Impact ionization processes in a photodriven Mott insulator: influence of phononic dissipation

### 2022-08-26 Paper1.tex
Final version Paolo 26.08.2022

We study a model for photovoltaic energy collection consisting of a Mott insulating layer in presence of acoustic phonons, coupled to two wide-band fermion leads at different chemical potentials and driven by a periodic electric field. We treat electron correlations with nonequilibrium dynamical mean-field theory (DMFT) using the so-called auxiliary master equation approach as impurity solver and include dissipation by acoustic phonons via the Migdal approximation. For a small hybridization to the leads, we obtain a peak in the photocurrent as a function of the driving frequency which can be associated with impact ionization processes.
For larger hybridizations the shallow peak suggests a suppression of impact ionization with respect to direct photovoltaic excitations. Acoustic phonons slightly enhance the photocurrent for small driving frequencies and suppress it at frequencies around the main peak 
% This effect occurs at all considered hybridization strengths.
 at all considered hybridization strengths.

@@

Experimentally, evidence for fast carrier multiplication processes has been detected via pump-probe experiments in VO$_2$~\cite{ho.bi.16}. Oxide heterostructures based on LaVO$_3$/SrTiO$_3$ have been identified as promising candidates, due to the ideal band gap and the strong polar field, able to separate the excited charge carriers~\cite{as.bl.13}. There are however some drawbacks, such as the low mobility of the carriers~\cite{wa.li.15,je.re.18}, which still put into question these materials’ applicability as efficient solar cells. Thus while a large-scale application of Mott-based solar cells may be difficult to achieve, employing them as photodetectors may be more promising on the long run, due to their high photoresponsivity. From the scientific point of view and for future applications it is thus worthwile to further investigate the properties of Mott-based photovoltaic materials and the mechanisms behind their inner workings, to explore whether alternative unexpected paths can be opened. In fact, a lot of theoretical work has been done to understand the II process (see, e.g.~\cite{co.ma.14,ec.we.11,ec.we.13,we.he.14,pe.be.19,so.do.18,ka.wo.20,ma.ev.22}).

@@

For this goal we consider the simplified model shown in Fig.~\ref{fig:setup}, consisting of a Hubbard layer located between two leads. The leads have themselves a wide band, as expected for good condutors, which are effectively narrowed due to the weak coupling to intermediate layers which we take as simplified models for the contacts. Electrons on the Hubbard layer interact locally with acoustic phonons. An external periodic electric field induces a Floquet steady state with a current flowing from the lead with the lower to the higher chemical potential, thus transferring its energy.
 We address this periodic problem
 via nonequilibrium Floquet dynamical mean-field theory (F-DMFT).

@@

Our goal is to investigate the occurrence of II in this photovoltaic setup and how it is affected by the presence of phonons. 
Specifically we study the behavior of the photovoltaic current, the spectral properties as well as the double occupation as a function of the hybridization strength and the properties of the phonons. Our analysis can only provide qualitative results, while quantitative comparisons with experimental systems require a more realistic setup and are beyond the scope of this work.
Our calculations show that a small hybridization to the leads is more favorable for II than a larger one. II therefore plays a crucial role in compensating the smaller charge injection, giving the same order of magnitude in the photocurrent as for the larger hybridization.
In all cases, the interaction with phonons slightly enhances the photocurrent for small driving frequencies, while suppressing it in vicinity of the main peak.

@@

Phonons are 
%The local e-ph coupling is
 included as in 
%EACOMM check, put also previous references
Ref.~\cite{ma.ga.22u} in the form of  acoustic  branches attached to each lattice site and coupled to the electrons via the Hamiltonian 
\begin{equation}\label{eq:e-ph_ham} 
\hat{H}_{\text{e-ph}} = g \sum_{i\sigma} \hat{n}_{i\sigma} \hat{x}_{i},  
\end{equation}
with $g$ as e-ph coupling and $\hat{x}_{i} \equiv \frac{1}{\sqrt{2}} \left( \hat{b}^{\dagger}_{i} + \hat{b}_i \right)$, where $\hat{b}^{\dagger}_{i}$ ($\hat{b}_{i}$) creates (annihilates) a phonon of the acoustic branch at site $i$, with dispersion relation described by $\hat{H}_{\text{ph}}$~\cite{ma.ga.22u}, see below.  
In contrast to Holstein phonons these have a finite bandwidth which is more effective in energy dissipation.
Details on the leads are provided in~\ref{sec:Dyson_equation}.

For mathematical simplicity~\cite{ge.ko.92,ao.ts.14}, 
 we consider the correlated central region as a $d$-dimensional layer and consider the limit of infinite dimensions $d \rightarrow \infty$ by rescaling the hopping as 
%EACOMM check parenthesis
$t_{\text{c}}=t^{\ast}/(2\sqrt{d})$. Taking $a=1$, sums over the crystal momentum ${\bf k}$ of a generic quantity $\chi$ read $\sum_{{\bf k}} \chi(\omega,{\bf k}) \rightarrow \int d\epsilon \int   d\overline{\epsilon} \ \rho(\epsilon,\overline{\epsilon}) \chi(\omega;\epsilon,\overline{\epsilon})$ with $\rho(\epsilon,\overline{\epsilon}) = (1/\pi t^{\ast 2}) \exp[-( \epsilon^{2} + \overline{\epsilon}^{2})/t^{\ast 2}]$ as the joint density of states~\cite{ts.ok.08} and with
% 
\begin{align}\label{eq:d-dim_crystal_dep}
\begin{split}  
\epsilon & = -2t_{\text{c}} \sum_{i=1}^{d} \cos(k_i a), \\  
\overline{\epsilon}& = -2t_{\text{c}}\sum_{i=1}^{d} \sin(k_i a). \\
\end{split}  
\end{align}
%

@@

% In Tommasos paper we also chose -q=1. Given the amplitude of the vector potential above, setting q=-1 allows us to take positive values of E_0 and Omega. same sign of j0 (see old draft). increasing the mu I have negative current meaning that particle/electric current is flowing in the opposite direction.

@@

The lattice Floquet GF of our setup obeys the Dyson equation 
\begin{equation}\label{eq:FullDysonEq}
\underline{{\bf G}}^{-1}(\omega_n;\epsilon,\overline{\epsilon}) = \underline{{\bf G}}^{-1}_{0}(\omega_n;\epsilon,\overline{\epsilon}) - \underline{{\bf \Sigma}}(\omega_n;\epsilon,\overline{\epsilon}) - \underline{{\bf \Sigma}}_{\text{e-ph}}(\omega_n;\epsilon,\overline{\epsilon}) \;,
\end{equation}
where in our approximation the electron-electron $ \underline{{\bf \Sigma}}(\omega_n;\epsilon,\overline{\epsilon})$ and electron-phonon $\underline{{\bf \Sigma}}_{\text{e-ph}}(\omega_n;\epsilon,\overline{\epsilon})$ self energies contribute independently to the total self energy~\footnote{In fact there is an indirect feedback via the DMFT self-consistency.}

@@

The electron self-energy (SE) $\underline{\bf{\Sigma}}$ is obtained from F-DMFT and therefore, in this approximation, independent of the crystal momentum, i.e. $\underline{\bf{\Sigma}}(\omega;\epsilon,\overline{\epsilon}) \simeq \underline{\bf{\Sigma}}(\omega)$. Further details are given in Sec.~\ref{sec:FDMFT_implementation}. 
In the same spirit, the e-ph SE is included locally as $\underline{\bf{\Sigma}}_{\text{e-ph}}(\omega;\epsilon,\overline{\epsilon}) \simeq \underline{\bf{\Sigma}}_{\text{e-ph}}(\omega)$. In terms of the Keldysh contour time arguments $z$ and $z^\prime$, it has the form

@@

We compute the electron SE in the Dyson Equation~\eqref{eq:FullDysonEq} using DMFT~\cite{me.vo.89,ge.ko.92,ge.ko.96}, and in particular its nonequilibrium Floquet extension F-DMFT~\cite{ts.ok.08,sc.mo.02u,jo.fr.08}. In DMFT the crystal momentum dependence of the electron SE is neglected, i.e. $\kel{\mat{\Sigma}}(\omega,\epsilon,\overline{\epsilon}) \to \kel{\mat{\Sigma}}(\omega)$. This allows us to map the original lattice problem onto a single-site impurity model with a bath hybridization function $\kel{\mat\Delta}(\omega)$ encoding the effect of all other lattice sites.

For completeness, we now
 briefly describe now the self-consistent F-DMFT scheme used.
(i) We start from an initial guess for the electron SE $\kel{\mat{\Sigma}}(\omega)$ and set $\kel{\mat \Sigma}_{\text{e-ph}}(\omega)=0$. (ii) Then we compute the local electron GF as 
%  
\begin{equation}\label{eq:Lat_LocGF}
\begin{split}
\kel{\mat G}_{\text{loc}}(\omega) &= \int \dd\epsilon \int \dd\overline{\epsilon} \ \rho(\epsilon,\overline{\epsilon}) \times \\ 
&\times \left[\kel{\mat G}^{-1}_{0}(\omega,\epsilon,\overline{\epsilon}) - \kel{\mat\Sigma}(\omega) - \kel{\mat \Sigma}_{\text{e-ph}}(\omega) \right]^{-1}.
\end{split}
\end{equation}
% 
(iii) Using Eq.~\eqref{eq:backbone_e-ph_SE}, we obtain the phonon contribution to the SE $\kel{\mat{\Sigma}}_{\text{e-ph}}(\omega)$.
(iv) The problem is mapped onto a single impurity plus bath, whose hybridization function
is given by
%
\begin{equation}\label{eq:imp_Dyson_eq}
\kel{\mat{\Delta}}(\omega) = \kel{\mat{g}}^{-1}_{0,\text{site}}(\omega) - \kel{\mat{G}}^{-1}_{\text{loc}}(\omega) - \kel{\mat{\Sigma}}(\omega),
\end{equation}   
%  
where $\kel{\mat{g}}^{-1}_{0,\text{site}}(\omega)$ is defined as in Eq.~\eqref{eq:inv_non-int_lat_GF_comps} with $\varepsilon_{mn}(\epsilon,\overline{\epsilon})=0$. (v) The nonequilibrium many-body impurity problem is solved according to the procedure in Sec.~\ref{sec:amea}, leading to the new
 $\kel{\mat{\Sigma}}(\omega)$. (vi) We insert the electron and e-ph SEs into step (ii) and iterate the steps (ii)-(vi) until convergence.

%EACOMM I eliminated this and the next subsubsection, is this okay?  
%\subsubsection{Floquet-diagonal self-energy approximation}
%\label{sec:FDSA}

%EACOMM check this paragraph, which I changed a bit
Eq.~\eqref{eq:imp_Dyson_eq} gives the bath hybridization function $\kel{\mat\Delta}(\omega)$ whose periodic time-dependence is encoded in its Floquet structure. 
This means that, in principle, one would have to solve a time-periodic impurity problem leading to a non-diagonal self-energy in general. However, in 
 Ref.~\cite{so.do.18} it was argued that for the electric field strengths considered, non-diagonal terms in the Floquet SE $\kel{\mat{\Sigma}}(\omega)$  can be safely neglected with respect to the diagonal ones. We follow this argument and adopt here 
this Floquet-diagonal self-energy approximation (FDSA) as well.
 In addition, it turns out that also for the 
 phonon SE $\underline{\bf{\Sigma}}_{\text{e-ph}}(\omega)$ this approximation is justified\footnote{More specifically, we have verified that in the parameters range in which FDSA is justified for the electron SE $\kel{\mat{\Sigma}}(\omega)$ (Sec.~\ref{sec:results}), the off-diagonal terms of the phonon SE $\underline{\Sigma}_{mm,\text{e-ph}}(\omega)$ are orders of magnitude smaller than the diagonal ones}. 
Consequently, we  have to solve a nonequilibrium stationary impurity problem, by using only the  $(0,0)$-Floquet matrix elements of $\kel{\mat{\Sigma}}(\omega)$ and $\kel{\mat\Delta}(\omega)$, 
%Eq.~\eqref{eq:imp_Dyson_eq}, 
as the other diagonal components can be reconstructed by using the property $\kel{\Sigma}_{mm}(\omega) = \kel{\Sigma}_{00}(\omega+m\Omega)$.

%\subsubsection{Auxiliary master equation approach}
%\label{sec:amea}

%We now
% briefly summarize the impurity solver used in step (v) of the DMFT self-consistent loop %described in Sec.~\ref{sec:FDMFT_implementation}. 
In order to solve the electron-electron many-body problem (step (v) of the DMFT self-consistent loop),
 we use the auxiliary master equation approach (AMEA)~\cite{ar.kn.13,do.nu.14,do.ga.15,do.so.17}, which we now briefly summarize. 
Therein, we map the impurity problem onto an auxiliary open quantum system (AOQS) consisting of a finite number of bath sites $N_{\text{B}}$ attached to Markovian reservoirs described by the Lindblad equation. The  hybridization function $\kel{\Delta}_{\text{aux}}(\omega)$ of this AOQS is obtained by fitting the original DMFT one. The key point is that the many-body problem of this AOQS can be solved exactly 
using standard many-body-diagonalization methods, as long as  $N_{\text{B}}$ is small.
The accuracy of this solution is set by the difference between
 $\kel{\Delta}_{\text{aux}}$ and $\kel{\Delta}$, which  becomes exponentially  small with increasing $N_{\text{B}}$.

@@

In order to study II in a Mott insulating layer, we adjust the bands to achieve the energy scheme shown in Fig.~\ref{fig:energy_setup}(a). 
 We follow Ref.~\cite{so.do.18} and take $U=12$ and unless stated otherwise $E_0=2$. The fermion leads and acoustic phonons have temperature $T=0.02$. We consider a particle-hole symmetric system with $\Gamma_{\text{l}}=\Gamma_{\text{r}}=0.37$, $t_{\text{l}}=t_{\text{r}}=1.7$, $\varepsilon_{\text{l}/\text{r}}=\mp 6$ and $v_{\text{l}}=v_{\text{r}}=v$. The parameters $t_{\text{l/r}}$, $\varepsilon_{\text{l/r}}$, and  $\Gamma_{\text{l/r}}$ are chosen such that the leads' DOS approximately overlaps with the Hubbard bands, i.e. they exhibit a \textquoteleft bandwidth\textquoteright~\footnote{Notice that the support of its spectrum is formally infinite. $W_{\text{b}}$ is the value at which the spectrum gets  suppressed.} $W_{\text{b}}\approx 8$ and are centered at the same position. The chemical potentials are set to $\mu_{\text{l}/\text{r}} =\mp 1$, so that a current from left to right is produced by energy taken from the driving.

Due to the hybridization with the leads, the local DOS of the Hubbard layer only features a pseudogap
 $\Delta_{\text{pg}} \approx 4$.
All simulations are carried out with the dimensionless factor $\alpha\equiv t_{r}E_0/\Omega^{2}<0.5$ for which the FDSA is justified~\footnote{In Ref.~\cite{so.do.18} the factor is defined as $\alpha=t_{c}E_0/\Omega^{2}$ and $t_{\text{c}}=1$. Setting $t_{r}=1$, we define for consistency $\alpha$ as in the main text.}.
% and first-order photon absorption processes are dominant.
 Whenever the electron-phonon interaction is included, we take $g=0.8$ and unless stated otherwise $\omega_{\text{ph}}=0.1$.

After some preliminary considerations in Sec.~\ref{sec:explicative_scheme}, we will discuss the occurrence of II at different $v$ first without (Sec.~\ref{sec:E0_2_only_electrons}) and then with coupling to acoustic phonons (Sec.~\ref{sec:E0_2_electrons_phonons}).

@@

\includegraphics[width=0.85\linewidth]{./figures_Paper1/energy_setup.pdf}
\caption{(Color online) Schematic representation of the processes occuring in the model considered. Red bands on the left and right describe the leads' DOS, where the dark color highlights occupied states and the light color empty states. Green bands are the LHB and UHB of the central layer. Due to the hybridization with the metallic leads only a pseudogap $\Delta_{\text{pg}}$ is present between the bands. 
 The vertical axis represents the energy. Panel (a) sketches the quantities introduced at the beginning of Sec.~\ref{sec:results}. Panel (b) illustrates a direct excitation process, in which an electron is excited by a photon with energy $\Omega$ (yellow arrow) to the UHB and escapes into the right lead (red arrow). Panel (c) displays an II process, where the photoexcited electron in the UHB excites a second electron from LHB to UHB (black arrows) and both escape into the right lead. In the nonequilibrium steady state considered here, only processes recovering the initial configuration are allowed.} 
\label{fig:energy_setup}
\end{figure}

\subsection{Qualitative Energy considerations and physical processes}
\label{sec:explicative_scheme}

To infer the conditions necessary for II, we consider the  scheme in Fig.~\ref{fig:energy_setup}. Thereby, we partially follow Ref.~\cite{so.do.18} for the electron-only (EO) case and extend the analysis to the case with e-ph interaction.
In comparison with Ref.~\cite{so.do.18} here the wide-band leads more realistically described a metallic structure. This makes the identification of II processes more subtle, as discussed below.
As in Ref.~\cite{so.do.18} we bypass transient behavior and consider directly the nonequilibrium Floquet steady state. In our analysis, we neglect higher-order processes such as multiparticle scattering processes.

@@

\begin{itemize}
\item For $\Omega<\Delta_{\text{pg}}$, 
we expect a strong suppression of the current
we do not expect any current if the DOS of the correlated layer has a true gap~\footnote{The remaining leak current can be either produced by multiple-photon absorption processes, which however, are strongly suppressed, or by the fact that there is no true gap}.
%To overcome a true gap with $\Omega<\Delta_{\text{pg}}$  should take place, but as written in the main text, such effects are negligible in the studied parameters range.}.

%~\footnote{To overcome a true gap with $\Omega<\Delta_{\text{pg}}$ multiple-photon absorption processes should take place, but as written in the main text, such effects are negligible in the studied parameters range.}. 
%If $\Delta_{\text{pg}}$ is a partial gap, we expect a suppression of the current.
\item For $\Delta_{\text{pg}}<\Omega<\Delta_{\text{pg}}+2W_{\text{b}}$ as shown in Fig.~\ref{fig:energy_setup}(b), an electron coming from the left lead into the LHB is photoexcited to the UHB and can escape directly into the right lead without additional scattering.  Such processes are often referred to as direct excitations (DEs).
\item For $2\Delta_{\text{pg}}<\Omega<\Delta_{\text{pg}}+2W_{\text{b}}$ as shown in Fig.~\ref{fig:energy_setup}(c), a photoexcited electron in the UHB can excite via II a second electron from LHB to UHB, before both escape into the right lead.
\item For $\Omega>\Delta_{\text{pg}}+2W_{\text{b}}$, there are no final states available for a photoexcited electron and we do not expect the transition to occur. 
\end{itemize}

>>>>

We study a model for photovoltaic energy collection consisting of a Mott insulating layer in presence of acoustic phonons, coupled to two wide-band fermion leads at different chemical potentials and driven %PGCH[
into a nonequilibrium steady state
%PGCH]
by a periodic electric field. We treat electron correlations with nonequilibrium dynamical mean-field theory (DMFT) using the so-called auxiliary master equation approach as impurity solver and include dissipation by acoustic phonons via the Migdal approximation. For a small hybridization to the leads, we obtain a peak in the photocurrent as a function of the driving frequency which can be associated with impact ionization processes.
For larger hybridizations the shallow peak suggests a suppression of impact ionization with respect to direct photovoltaic excitations. Acoustic phonons slightly enhance the photocurrent for small driving frequencies and suppress it at frequencies around the main peak at all considered hybridization strengths.

@@

Experimentally, evidence for fast carrier multiplication processes has been detected via pump-probe experiments in VO$_2$~\cite{ho.bi.16}. Oxide heterostructures based on LaVO$_3$/SrTiO$_3$ have been identified as promising candidates, due to the ideal band gap and the strong polar field, able to separate the excited charge carriers~\cite{as.bl.13}. There are however some drawbacks, such as the low mobility of the carriers~\cite{wa.li.15,je.re.18}, which still put into question these materials’ applicability as efficient solar cells. Thus while a large-scale application of Mott-based solar cells may be difficult to achieve, employing them as photodetectors may be more promising on the long run, due to their high photoresponsivity. From the scientific point of view and for future applications it is thus worthwile to further investigate the properties of Mott-based photovoltaic materials and the mechanisms behind their inner workings, to explore whether alternative unexpected paths can be opened. In fact, a lot of theoretical work has been done to understand the II process (see, e.g.~\cite{co.ma.14,ec.we.11,ec.we.13,we.he.14,pe.be.19,so.do.18,ka.wo.20,mano.19,ma.ev.22}).

@@

For this goal we consider the simplified model shown in Fig.~\ref{fig:setup}, consisting of a Hubbard layer located between two leads. The leads have themselves a wide band, as expected for good conductors, which is effectively narrowed due to the weak coupling to intermediate layers which we take as simplified models for the contacts. Electrons on the Hubbard layer interact locally with acoustic phonons. An external periodic electric field induces a Floquet steady state with a current flowing from the lead with the lower to the lead with the higher chemical potential, thus transferring its energy.
 We address this periodic problem via nonequilibrium Floquet dynamical mean-field theory (F-DMFT).

@@

Our goal is to investigate the occurrence of II in this photovoltaic setup and how it is affected by the presence of phonons. Specifically, we study the behavior of the photovoltaic current, the spectral properties as well as the double occupation as a function of the hybridization strength and the properties of the phonons. Our analysis can only provide qualitative results, while quantitative comparisons with experimental systems require a more realistic setup and are beyond the scope of this work.

Our calculations show that a small hybridization to the leads is more favorable for II than a larger one. II therefore plays a crucial role in compensating the smaller charge injection, giving the same order of magnitude in the photocurrent as for the larger hybridization.
In all cases, the interaction with phonons slightly enhances the photocurrent for small driving frequencies, while suppressing it in vicinity of the main peak.

@@

As in Ref.~\cite{ma.ga.22u}, phonons are included in the form of acoustic  branches attached to each lattice site and coupled to the electrons via the Hamiltonian 
\begin{equation}\label{eq:e-ph_ham} 
\hat{H}_{\text{e-ph}} = g \sum_{i\sigma} \hat{n}_{i\sigma} \hat{x}_{i},  
\end{equation}
with $g$ as e-ph coupling and $\hat{x}_{i} \equiv \frac{1}{\sqrt{2}} \left( \hat{b}^{\dagger}_{i} + \hat{b}_i \right)$, where $\hat{b}^{\dagger}_{i}$ ($\hat{b}_{i}$) creates (annihilates) a phonon of the acoustic branch at site $i$, with dispersion relation described by $\hat{H}_{\text{ph}}$, discussed in Sec~\ref{sec:Dyson_equation}. In contrast to Holstein phonons, they have a finite bandwidth, which is more effective in energy dissipation. Details on the leads are provided in Sec.~\ref{sec:Dyson_equation}.

For mathematical simplicity~\cite{ge.ko.92,ao.ts.14}, 
 we consider the correlated central region as a $d$-dimensional layer and consider the limit of infinite dimensions $d \rightarrow \infty$ by rescaling the hopping as $t_{\text{c}}=t^{\ast}/(2\sqrt{d})$. Taking $a=1$, sums over the crystal momentum ${\bf k}$ of a generic quantity $\chi$ read $\sum_{{\bf k}} \chi(\omega,{\bf k}) \rightarrow \int d\epsilon \int   d\overline{\epsilon} \ \rho(\epsilon,\overline{\epsilon}) \chi(\omega;\epsilon,\overline{\epsilon})$ with $\rho(\epsilon,\overline{\epsilon}) = (1/\pi t^{\ast 2}) \exp[-( \epsilon^{2} + \overline{\epsilon}^{2})/t^{\ast 2}]$ as the joint density of states~\cite{ts.ok.08} and with
% 
\begin{align}\label{eq:d-dim_crystal_dep}
\begin{split}  
\epsilon & = -2t_{\text{c}} \sum_{i=1}^{d} \cos(k_i a), \\  
\overline{\epsilon}& = -2t_{\text{c}}\sum_{i=1}^{d} \sin(k_i a). \\
\end{split}  
\end{align}
%

@@

@@

The lattice Floquet GF of our setup obeys the Dyson equation 
\begin{equation}\label{eq:FullDysonEq}
\underline{{\bf G}}^{-1}(\omega_n;\epsilon,\overline{\epsilon}) = \underline{{\bf G}}^{-1}_{0}(\omega_n;\epsilon,\overline{\epsilon}) - \underline{{\bf \Sigma}}(\omega_n;\epsilon,\overline{\epsilon}) - \underline{{\bf \Sigma}}_{\text{e-ph}}(\omega_n;\epsilon,\overline{\epsilon}),
\end{equation}
where in our approximation the electron self-energy (SE) $ \underline{{\bf \Sigma}}$ and e-ph SE $\underline{{\bf \Sigma}}_{\text{e-ph}}$ contribute independently to the total SE~\footnote{In fact, there is an indirect feedback via the DMFT self-consistency.}.

@@

The electron SE $\underline{\bf{\Sigma}}$ is obtained from F-DMFT and therefore, in this approximation, independent of the crystal momentum, i.e. $\underline{\bf{\Sigma}}(\omega;\epsilon,\overline{\epsilon}) \simeq \underline{\bf{\Sigma}}(\omega)$. Further details are given in Sec.~\ref{sec:FDMFT_implementation}. In the same spirit, the e-ph SE is included locally as $\underline{\bf{\Sigma}}_{\text{e-ph}}(\omega;\epsilon,\overline{\epsilon}) \simeq \underline{\bf{\Sigma}}_{\text{e-ph}}(\omega)$. In terms of the Keldysh contour time arguments $z$ and $z^\prime$, it has the form

@@

We compute the electron SE in the Dyson equation~\eqref{eq:FullDysonEq} using DMFT~\cite{me.vo.89,ge.ko.92,ge.ko.96}, and in particular its nonequilibrium Floquet extension F-DMFT~\cite{ts.ok.08,sc.mo.02u,jo.fr.08}. In DMFT the crystal momentum dependence of the electron SE is neglected, i.e. $\kel{\mat{\Sigma}}(\omega,\epsilon,\overline{\epsilon}) \to \kel{\mat{\Sigma}}(\omega)$. This allows us to map the original lattice problem onto a single-site impurity model with a bath hybridization function $\kel{\mat\Delta}(\omega)$ encoding the effect of all other lattice sites.

For completeness, we now
 briefly describe the self-consistent F-DMFT scheme used.
(i) We start from an initial guess for the electron SE $\kel{\mat{\Sigma}}(\omega)$ and set $\kel{\mat \Sigma}_{\text{e-ph}}(\omega)=0$. (ii) Then we compute the local electron GF as 
%  
\begin{equation}\label{eq:Lat_LocGF}
\begin{split}
\kel{\mat G}_{\text{loc}}(\omega) &= \int \dd\epsilon \int \dd\overline{\epsilon} \ \rho(\epsilon,\overline{\epsilon}) \times \\ 
&\times \left[\kel{\mat G}^{-1}_{0}(\omega,\epsilon,\overline{\epsilon}) - \kel{\mat\Sigma}(\omega) - \kel{\mat \Sigma}_{\text{e-ph}}(\omega) \right]^{-1}.
\end{split}
\end{equation}
% 
(iii) Using Eq.~\eqref{eq:backbone_e-ph_SE}, we obtain the phonon contribution to the SE $\kel{\mat{\Sigma}}_{\text{e-ph}}(\omega)$.
(iv) The problem is mapped onto a single impurity plus bath, whose hybridization function
is given by
%
\begin{equation}\label{eq:imp_Dyson_eq}
\kel{\mat{\Delta}}(\omega) = \kel{\mat{g}}^{-1}_{0,\text{site}}(\omega) - \kel{\mat{G}}^{-1}_{\text{loc}}(\omega) - \kel{\mat{\Sigma}}(\omega),
\end{equation}   
%  
where $\kel{\mat{g}}^{-1}_{0,\text{site}}(\omega)$ is defined as in Eq.~\eqref{eq:inv_non-int_lat_GF_comps} with $\varepsilon_{mn}(\epsilon,\overline{\epsilon})=0$. (v) The nonequilibrium many-body impurity problem is solved according to the procedure described below, leading to the new $\kel{\mat{\Sigma}}(\omega)$. (vi) We insert the electron and e-ph SEs into step (ii) and iterate the steps (ii)-(vi) until convergence.

%PGCH[ I changed some words and rephrased the last sentence in this paragraph after Enrico modified it

Eq.~\eqref{eq:imp_Dyson_eq} gives a bath hybridization function $\kel{\mat\Delta}(\omega)$ whose periodic time-dependence is encoded in its Floquet structure. 
This means that, in principle, one should solve a time-periodic impurity problem leading to a non-diagonal SE. However, in Ref.~\cite{so.do.18} it was argued and shown that for the considered electric field amplitudes, off-diagonal terms in the electron SE $\kel{\mat{\Sigma}}(\omega)$ can be safely neglected with respect to the diagonal ones. We follow this argument and adopt here 
this Floquet-diagonal self-energy approximation (FDSA) as well. In addition, it turns out that also for the 
 phonon SE $\underline{\bf{\Sigma}}_{\text{e-ph}}(\omega)$ this approximation is justified~\footnote{More specifically, we verified that in the parameters range in which FDSA is justified for the electron SE $\kel{\mat{\Sigma}}(\omega)$ (Sec.~\ref{sec:results}), the off-diagonal terms of the phonon SE $\underline{\bf{\Sigma}}_{\text{e-ph}}(\omega)$ are orders of magnitude smaller than the diagonal ones}. 
Consequently, we  solve a nonequilibrium stationary impurity problem, by considering only the $(0,0)$-Floquet matrix element of all the quantities in Eq.~\eqref{eq:imp_Dyson_eq}. The other diagonal components of the SEs are then reconstructed by using the property $\kel{\Sigma}_{mm}(\omega) = \kel{\Sigma}_{00}(\omega+m\Omega)$.

%PGCH]

In order to solve the many-body problem in step (v) of the DMFT self-consistent loop, we use the auxiliary master equation approach (AMEA)~\cite{ar.kn.13,do.nu.14,do.ga.15,do.so.17}, which we now briefly summarize. Therein, we map the impurity problem onto an auxiliary open quantum system (AOQS) consisting of a finite number of bath sites $N_{\text{B}}$ attached to Markovian reservoirs described by the Lindblad equation. The  hybridization function $\kel{\Delta}_{\text{aux}}(\omega)$ of this AOQS is obtained by fitting the original DMFT one. The key point is that the many-body problem of this AOQS can be solved exactly using standard many-body-diagonalization methods, as long as  $N_{\text{B}}$ is small. The accuracy of this solution is set by the difference between $\kel{\Delta}_{\text{aux}}$ and $\kel{\Delta}$, which  becomes exponentially  small with increasing $N_{\text{B}}$.

@@

In order to study II in a Mott insulating layer, we adjust the bands to achieve the energy scheme shown in Fig.~\ref{fig:energy_setup}(a). 
 We follow Ref.~\cite{so.do.18} and take $U=12$ and unless stated otherwise $E_0=2$. The fermion leads and the acoustic phonons have temperature $T=0.02$. We consider a particle-hole symmetric system with $\Gamma_{\text{l}}=\Gamma_{\text{r}}=0.37$, $t_{\text{l}}=t_{\text{r}}=1.7$, $\varepsilon_{\text{l}/\text{r}}=\mp 6$ and $v_{\text{l}}=v_{\text{r}}=v$. The parameters $t_{\text{l/r}}$, $\varepsilon_{\text{l/r}}$, and  $\Gamma_{\text{l/r}}$ are chosen such that the leads' DOS approximately overlaps with the Hubbard bands, i.e. they exhibit a \textquoteleft bandwidth\textquoteright~\footnote{Notice that the support of its spectrum is formally infinite. $W_{\text{b}}$ is the value at which the spectrum gets  suppressed.} $W_{\text{b}}\approx 8$ and are centered at the same position. The chemical potentials are set to $\mu_{\text{l}/\text{r}} =\mp 1$, so that a current from left to right is produced by taking energy from the driving.

Due to the hybridization with the leads, the local DOS of the Hubbard layer only features a pseudogap
 $\Delta_{\text{pg}} \approx 4$.
All simulations are carried out with the dimensionless factor $\alpha\equiv t_{r}E_0/\Omega^{2}<0.5$ for which the FDSA is justified~\footnote{In Ref.~\cite{so.do.18} the factor is defined as $\alpha=t_{c}E_0/\Omega^{2}$ and $t_{\text{c}}=1$. Setting $t_{r}=1$, we define for consistency $\alpha$ as in the main text.}. Whenever the electron-phonon interaction is included, we take $g=0.8$ and unless stated otherwise $\omega_{\text{ph}}=0.1$.

After some preliminary considerations in Sec.~\ref{sec:explicative_scheme}, we discuss the occurrence of II at different $v$ first without (Sec.~\ref{sec:E0_2_only_electrons}) and then with coupling to acoustic phonons (Sec.~\ref{sec:E0_2_electrons_phonons}).

@@

\includegraphics[width=0.8\linewidth]{./figures_Paper1/energy_setup.pdf}
\caption{(Color online) Schematic representation of the processes occuring in the model considered. Red bands on the left and right describe the leads' DOS, where the dark color highlights occupied states and the light color empty states. Green bands are the LHB and UHB of the central layer. The vertical axis represents the energy. Due to the hybridization with the metallic leads only a pseudogap $\Delta_{\text{pg}}$ is present between the Hubbard bands. Panel (a) sketches the quantities introduced at the beginning of Sec.~\ref{sec:results}. Panel (b) illustrates a direct excitation process, in which an electron is excited by a photon with energy $\Omega$ (yellow arrow) to the UHB and escapes into the right lead (red arrow). Panel (c) displays an II process, where the photoexcited electron in the UHB excites a second electron from LHB to UHB (black arrows) and both escape into the right lead. In the nonequilibrium steady state considered here, only processes recovering the initial configuration are allowed.} 
\label{fig:energy_setup}
\end{figure}

\subsection{Qualitative energy considerations and physical processes}
\label{sec:explicative_scheme}

To infer the conditions necessary for II, we consider the  scheme in Fig.~\ref{fig:energy_setup}. Thereby, we partially follow Ref.~\cite{so.do.18} for the electron-only (EO) case and extend the analysis to the case with e-ph interaction.
In comparison with Ref.~\cite{so.do.18}, here the wide-band leads describe more realistically a metallic structure. This makes the identification of II processes more subtle, as discussed below.
As in Ref.~\cite{so.do.18} we bypass transient behavior and consider directly the Floquet steady state. In our analysis, we neglect higher-order processes such as multiparticle scattering processes.

@@

\begin{itemize}
\item For $\Omega<\Delta_{\text{pg}}$, 
we expect a strong suppression of the current~\footnote{The remaining leak current can be either produced by multiple-photon absorption processes, which however, are strongly suppressed, or by the fact that there is no true gap} and
we do not expect any current if the DOS of the correlated layer has a true gap.
\item For $\Delta_{\text{pg}}<\Omega<\Delta_{\text{pg}}+2W_{\text{b}}$ as shown in Fig.~\ref{fig:energy_setup}(b), an electron coming from the left lead into the LHB is photoexcited to the UHB and can escape directly into the right lead without additional scattering.  Such processes are often referred to as direct excitations (DEs).
\item For $2\Delta_{\text{pg}}<\Omega<\Delta_{\text{pg}}+2W_{\text{b}}$ as shown in Fig.~\ref{fig:energy_setup}(c), a photoexcited electron in the UHB can excite via II a second electron from LHB to UHB, before both escape into the right lead.
\item For $\Omega>\Delta_{\text{pg}}+2W_{\text{b}}$, there are no final states available for a photoexcited electron and we do not expect the transition to occur. 
\end{itemize}

Notice that in the energy window $\Delta_{\text{pg}}<\Omega<2\Delta_{\text{pg}}$ the only scattering processes taking place are DEs, while for $2\Delta_{\text{pg}}<\Omega<\Delta_{\text{pg}}+2W_{\text{b}}$, both DE and II can occur. 
This is in contrast to the case of Ref.~\cite{so.do.18}, in which the peculiar ad-hoc narrow leads' bands only allow for II processes in a certain $\Omega$-range.
For this reason, and due to the fact that the boundaries of these energy ranges are not strict, it is more tricky to disentangle these physical processes in the present case.
